---
title: "Running the texmex, margarita and lmr test suites"
author: "Harry Southworth"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    css: /home/harry/MEGAsync/work/general/css/report.css
    toc: true
    toc_depth: 3
    fig_caption: yes
    fig_width: 7
    fig_height: 5
subparagraph: true
always_allow_html: yes
bibliography: /home/harry/MEGAsync/work/general/bibliography/bibliography.bib
---

```{r setup, include=FALSE}
seed <- 20220517
set.seed(seed)
gitcv <- render::gitcv
here <- here::here

options(scipen = 10^6)
knitr::opts_chunk$set(echo = TRUE)
options(dplyr.summarise.inform = FALSE)

library(texmex)
library(margarita)
library(lmr)
library(tinytest)

source(here("R/run_test_file.R"))

theFormat <- "html"
```

# {.tabset}


## Introduction
The <a href="https://github.com/harrysouthworth/texmex">texmex</a> [@texmex],
<a href="https://github.com/harrysouthworth/margarita">margarita</a> and
<a href="https://github.com/harrysouthworth/lmr">lmr</a>
packages have testing suites that rely on
the testthat package [@testthat]. The test suites don't currently run,
apparently due to changes in testthat.

Here, we run versions of the texmex test functions that depend not on testthat,
but on tinytest [@tinytest].

Output appears below, followed by a summary of the R session.

The plots appear in the pdf file.

## Results {.tabset}

### texmex

```{r, echo = TRUE, message = FALSE}
testFiles <- paste0("R/texmex/", list.files(here::here("R/texmex")))
length(testFiles)
tail(testFiles)
```

So there are `r length(testFiles)` test scripts. The whole thing fails if
any tests are failed, so scroll to the bottom and see if all the scripts
ran.

```{r, echo = TRUE, message = FALSE}
pdf("texmex_plots.pdf")
for (i in 1:length(testFiles)){
  cat(paste0("\n############## ", i, " ", testFiles[i], " ##############\n"))
  o <- run_test_file(here(testFiles[i]), verbose = FALSE)
  print(summary(o))
}
dev.off()
```

### margarita

```{r, echo = TRUE, message = FALSE}
testFiles <- paste0("R/margarita/", list.files(here::here("R/margarita")))
length(testFiles)

## Scroll to the bottom to see if all the test scripts ran.

pdf("margarita_plots.pdf")
for (i in 1:length(testFiles)){
  cat(paste0("\n############## ", i, " ", testFiles[i], " ##############\n"))
  o <- run_test_file(here(testFiles[i]), verbose = FALSE)
  print(summary(o))
}
dev.off()
```

### lmr

The lmr tests don't include any figures, so we don't need to open a pdf
device here.

```{r, echo = TRUE}
testFiles <- paste0("R/lmr/", list.files(here("R/lmr")))
length(testFiles)

for (i in 1:length(testFiles)){
  cat(paste0("\n############## ", i, " ", testFiles[i], " ##############\n"))
  o <- run_test_file(here(testFiles[i]), verbose = FALSE)
  print(summary(o))
}
```


## Appendix

### Information on the R session
Information on the R session, in the interests of reproducibility.
```{r sessioninfo, echo=FALSE}
pander::pander(sessionInfo())
```

### References
